Periodograms for Multiband Astronomical Time Series

### 2015-01-28 writeup/paper.tex
update paper: multiband_LS -> gatspy

\appendix
\section{{\tt multiband\_LS}: Python Implementation of Multiband Periodogram}
\sectlabel{multiband_LS}
The algorithm outlined in this paper is available as an open-source Python package\footnote{\url{http://github.com/jakevdp/multiband_LS/}}, along with code to download the data and recreate all the figures in this paper.
{\tt multiband\_LS} is a pure-Python package written to be compatible with both Python 2 and Python 3, and performs fast numerical computation through dependencies on {\tt numpy} \citep{numpy}\footnote{\url{http://www.numpy.org}} and {\tt astroML} \citep{astroML}\footnote{\url{http://www.astroml.org}}, which offer optimized implementatinos of numerical methods in Python.

@@

\begin{lstlisting}
from multiband_LS import LombScargleMultiband
import numpy as np

# Fetch the Sesar 2010 RR Lyrae data
from multiband_LS.data import fetch_rrlyrae
data = fetch_rrlyrae()
t, mag, dmag, filts = data.get_lightcurve(data.ids[0],
                                          return_1d=True)

@@

\begin{lstlisting}
from multiband_LS import SuperSmoother

@@

# Compute power at the following periods
power = model.periodogram(periods)
\end{lstlisting}

The models in the \texttt{multiband\_LS} package contain many more methods, and much more functionality that what is shown here. For updates, more examples, and more information, visit \url{http://github.com/jakevdp/multiband_LS}.

>>>>

\appendix
\section{Python Implementation of Multiband Periodogram}
\sectlabel{gatspy}
The algorithm outlined in this paper is available in {\tt gatspy}, an open-source Python package for general astronomical time-series analysis\footnote{\url{http://github.com/jakevdp/gatspy/}}. Along with the periodogram implementation, it also contains code to download all the data used in this work. Code to reproduce this paper, including all figures, is available as well\footnote{\url{http://github.com/jakevdp/multiband_LS/}}.

{\tt gatspy} is a pure-Python package written to be compatible with both Python 2 and Python 3, and performs fast numerical computation through dependencies on {\tt numpy} \citep{numpy}\footnote{\url{http://www.numpy.org}} and {\tt astroML} \citep{astroML}\footnote{\url{http://www.astroml.org}}, which offer optimized implementatinos of numerical methods in Python.

@@

\begin{lstlisting}
from gatspy.periodic import LombScargleMultiband
import numpy as np

# Fetch the Sesar 2010 RR Lyrae data
from gatspy.datasets import fetch_rrlyrae
data = fetch_rrlyrae()
t, mag, dmag, filts = data.get_lightcurve(data.ids[0])

@@

\begin{lstlisting}
from gatspy.periodic import SuperSmoother

@@

# Compute power at the given periods
power = model.periodogram(periods)
\end{lstlisting}

The models in the \texttt{gatspy} package contain many more methods, and much more functionality that what is shown here. For updates, more examples, and more information, visit \url{http://github.com/jakevdp/gatspy/}.
